Comparison of long and short amplicon metabarcoding to determination of fungal species diversity and spatial turnover in an ectomycorrhizal West African woodland

### 2019-08-11 writing/MSA2019_presentation.Rnw
copy presentation for Anna's group as base for MSA presentation.

\title{Turnover scale of soil fungal community composition}
\subtitle{Presentation for Anna's Group Meeting}
\author{Brendan Furneaux}
\date{26 April, 2019}

@@

>>>>

\title{Comparison of long and short amplicon metabarcoding to determination of fungal species diversity and spatial turnover in an ectomycorrhizal West African woodland}
\subtitle{Presentation for Anna's Group Meeting}
\author{Brendan Furneaux, Mohammad Bahram, Nourou Yorou, Anna Rosling, Martin Ryberg}
\date{13 August, 2019}

@@

# Metabarcoding

  - Cloning + Sanger -> 454 -> Illumina
  - For fungi, usually ITS2
      - short
      - intraspecific variation in most groups
      - good database support (Unite 8.0 - 817 130 fungal sequences)
      - ITS is "official barcode for fungi" \cite{schoch2012}
      - fungal specific primers
  - problems
      - not alignable
      - cannot place unknown sequences
      - variant 5.8S
      - variable length

  - LSU (26S/28S)
      - alternating highly conserved domains and variable regions
      - widely used for phylogenies
      - universal primers
      - less variable length
      - more conserved than ITS
      - not as good database support (RDP 11 fungal LSU - 125 525, Silva 132 LSU 907 382 of which )
  - SSU (18S)
      - alternating highly conserved and variable regions
      - more conserved than LSU
      - used for barcoding prokaryotes and "protists"
      - good database support (Silva SSU), but not as good for fungi
